%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Jason}{Antic}{ % Your name
\href{mailto:jsa169@gmail.com}{jsa169@gmail.com} | 858.699.9841 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Summary
%------------------------------------------------

\section{Summary} 

I'm a software engineer who loves his craft, and desires to make a real world impact. I am a "Jack of All Trades" (and master of some).  I am sought out quite often for help on "head-scratcher" type problems.  \\

I aim for my code to read like a book. I optimize my efforts on communication in code, first and foremost. I prioritize pragmatic decision making over "shoulds".  I'm a big advocate of testing and static analysis tools. 

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Pennsylvania State \newline University}

\descript{BS in Computer Science \newline Minor in Mathematics}
\location{2003 - 2006 | State College, PA}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 

Github: \href{http://github.com/jantic}{\bf http://github.com/jantic} \\
LinkedIn: \href{http://www.linkedin.com/in/jason-antic-73940698/}{\bf http://www.linkedin.com/in/jason-antic-73940698} \\

\sectionspace % Some whitespace after the section
%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming Languages}
\textbf{Primary:}\newline 
Java \textbullet{} JavaScript \textbullet{} SQL \textbullet{} C\# \textbullet{} HTML \textbullet{} Regex \\ 
\textbf{Have Used:}\newline 
Perl \textbullet{} Python \textbullet{} VB.NET \textbullet{} CSS \textbullet{} C/C++ \\

\sectionspace % Some whitespace after the section

\subsection{Libraries and APIs}

\textbf{Primary:}\newline 
jQuery \textbullet{} AJAX \textbullet{} JUnit \textbullet{} Guava \textbullet{} Selenium \textbullet{} AutoIt \\ 
\textbf{Have Used:}\newline 
Keras \textbullet{} Tensorflow \textbullet{} REST \textbullet{} LINQ \textbullet{} Spring \\
\sectionspace % Some whitespace after the section

\subsection{Tools}

\textbf{Primary:}\newline 
Eclipse \textbullet{} Visual Studio \textbullet{} Microsoft Excel \newline SQL Server Management Studio \\ 
\textbf{Have Used:}\newline 
IntelliJ IDEA \textbullet{} ANTS Profiler \newline YourKit Profiler \textbullet{} Komodo IDE \newline Amazon Web Services (AWS) \textbullet{} Microsoft Azure\\

\sectionspace % Some whitespace after the section


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.64\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Arrowhead General Insurance Agency}

\descript{Software Engineer}

\location{November 2014 – Present | San Diego, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Full stack development: Java/SQL/JavaScript/HTML
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Designed our software engineer candidate take-home and whiteboard tests.
\item Gave talks on problem solving, QA automation, and JUnit. 
\item Project:  Java-based scripting rules engine (statically compiled rules, dynamically modifiable at runtime).
\item Project:  Migration of our insurance calculation engine to latest version (Perl).
\item Project:  Internal compile/deploy tool for our insurance rating engine (C\#).
\end{tightitemize}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\descript{Automation Engineer}

\location{January 2013 – November 2014 | San Diego, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space 
Continued to develop for Tellurium
\begin{tightitemize}
\item Drove cultural change of delegating automation work to QAs as C\# script and Excel spreadsheet authors, to greatly increase productivity and utilize their domain knowledge.
\item Mentored new automation engineers.
\item Led the QA team to adopt improved quality assurance automation practices.
\end{tightitemize}

\sectionspace % Some whitespace after the section
%------------------------------------------------
\descript{Software Developer}

\location{June 2010 – January 2013 | San Diego, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Full stack development: Java/SQL/JavaScript/HTML
\begin{tightitemize}
\item Introduced the company's use of jQuery/AJAX/HTML5 based web pages.
\item Introduced the extensive use of JUnit tests for our team.
\item Project: Excel based document trigger rules web service.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\descript{Automation Engineer}

\location{June 2009 - June 2010 | San Diego, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space 
Created Tellurium, our QuickTest Professional (QTP) replacement.
\begin{tightitemize}
\item Developed highly reliable, data-driven test automation.
\item Automated testing of PDFs, insurance calculations, and user interface.
\end{tightitemize}

\sectionspace % Some whitespace after the section
%------------------------------------------------

\descript{Quality Assurance Analyst}

\location{October 2007 – June 2009 | San Diego, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space

%------------------------------------------------

\runsubsection{Volunteer Work}
\descript{\newline First Robotics Mentor}

\location{January 2014 – Present | Kearny High School | San Diego, CA}
\begin{tightitemize}
\item Java based robot code.
\item Focused on computer vision. 
\end{tightitemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space

%------------------------------------------------

\runsubsection{Side Projects}
\descript{}
\location{See Github Link}
\begin{tightitemize}
\item Fast.AI Deep Learning course. CNNs and RNNs, in Python/Keras. (2017- in progress).
\item "What is That?"- Program that recognizes mammalian species in photos around the world based on Clarifai API, Wolfram Alpha taxonomic data, and species geographic distribution.  C\# (2014).
\item "Intelligent Media Player"- Generated music playlists based on Last.fm user preference statistics.  VB.NET (2010).
\end{tightitemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column
\end{document}